\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Sourabh,
    middleinitial=R,
    lastname=Dattawad,
    email=sourabhdattawad@gmail.com,
    phone=(+49)152-313-88640,
    linkedin=sourabhdattawad,
    github=sourabhdattawad,
    website=sourabhdattawad,
    city=Stuttgart,
    state=BW,
    fixobjectivespacing=true,
]

\objective{I am a Machine Learning Engineer with over 4 years of work experience. Presently, I am enrolled in a master's program in computational linguistics (NLP) at the University of Stuttgart. I am seeking part-time working student opportunities, particularly in the fields of Large Language Models (LLMs) and Generative Artificial Intelligence (GenAI).}

% ----- Education -----
\section{Education}

\experience{Master of Science}{Computational Linguistics (NLP)}{Apr
    2023}{Current}{
    \noindent Institute for Natural Language Processing
    \hfill GPA: 2.1 \newline
    Universität Stuttgart, Stuttgart, BW
}

\experience{Bachelor of Science}{Computer Science}{Aug 2014}{May 2018}{
    \noindent Visvesvaraya Technological University (VTU), Karnataka, India
    \hfill GPA: Distinction
}
% ----- SKILLS -----
\section{Skills}

\begin{itemize}
    \item Programming Languages: {Python}
    \item Data Engineering: {Apache - Pyspark, Flink, Hive, AirFlow}
    \item Cloud:  Amazon Web Services (AWS) - S3, Lambda, Kinesis, SageMaker
    \item Databases: {SQL/No-SQL/Vector Databases, Weaviate, Elasticsearch, PostgreSQL, MongoDB, InfluxDB}
    \item NLP \& Machine Learning: {Large Language Models (LLMs),
          OpenAI API, HuggingFace, LangChain, Prompt Engineering, RAGs, Spacy,
          ScikitLearn, Numpy, Tensorflow, Pytorch, NLTK, Pandas}
    \item Visualization \& Monitoring: {Grafana, Metabase, Kibana, Plotly, Matplotlib, Weights \& Biases }
    \item CI/CD: {Git, Gitlab}
\end{itemize}

% ----- Work Experience -----
\section{Work Experience}

\experience{Machine Learning Engineer - 3}{Cisco Systems}{Oct 2020}{Mar 2023}{
    \achievement{

        Developed an algorithm to classify user devices into groups for efficient network management at a scale of 2M+ devices per week.

    }
    \achievement{

        Designed a deep learning based spoofing detection model with accuracies ranging from 80\%-92\% across different device classes like phones, printers, cameras etc.

    }
    \achievement{

        Deployed ETL jobs to process over 20 Million data points every day using Pyspark and Airflow.

    }
    \achievement{

        Built grafana dashboards to visualize predictions, user interactions and tracking model quality in production.

    }
    \achievement{

        Improved unit test coverage by 25\% in Pytest and further implemented integration tests to check the correctness of ML systems.

    }
    \achievement{

        Implemented Hive queries to monitor customer data quality in Looker, resulting in data quality improvement in the range of 20-50\% for 1000+ customers.

    }

}
\experience{Machine Learning Engineer}{Mercedes-Benz R\&D India}{Aug
    2018}{Oct 2020 }{
    \achievement{

        Developed a machine learning algorithm for identifying high
        business impact incidents with an accuracy of 90+\%, reducing
        production downtime by at least 50 hours per month.

    }
    \achievement{

        Created context-based embeddings for 2000+ entities involved in the production of automobiles to compare and prioritize critical systems.

    }
    \achievement{

        Implemented topic modelling and issue extraction using data mining and NLP techniques involving Mercedes-Me app review data and consumer complaint data for efficient problem management.

    }
}
\experience{Machine Learning Intern}{Indian Council of Medical Research}{Jan
    2018}{July 2018 }{
    \achievement{

        Analyzed dengue disease trend by identifying the top 3 environmental factors that influence the growth of the virus.

    }
    \achievement{

        Developed an ensemble of models to predict the type of cancer with a 90\% accuracy(F-beta) score along with model explainability using LIME.

    }
}
\experience{Software Engineer Intern}{Sportzify}{Oct
    2015}{MAR 2017 }{
    \achievement{

        Developed and integrated a real-time notification system using Socket.io to streamline communication and enhance user experience.

    }
    \achievement{

        Integrated payment gateway and developed a comprehensive service
        for managing referrals, coupons, discounts, refunds, etc.,
        facilitating over 1000 monthly transactions.
    }
}
% ----- Technical Projects -----
\section{Technical Projects}

\experience{Expressive Resume}{Personal Project}{Nov 2021}{Dec 2021}{
    \achievement{

        Created a \tech{\LaTeX} class that makes it easy for anyone to
        quickly create a beautiful resume and cover letter.

    }
}


% ----- Education -----
\section{Publications \& Conferences}

\experience{FOSSCON}{Deep learning for Computer Vision and Natural Language Processing}{}{July 2019}{
    \noindent Gogte Institute of Technology, Belagavi, India
}

\experience{BAICONF}{How vectorizing business-critical entities help solve operational problems}{}{Dec 2019}{
    \noindent Indian Institute of Management, Bengaluru, India
}

% \experience{How vectorizing business-critical entities help solve operational problems}{Aug 2018}{}{
%     \noindent  \newline Institute for Natural Language Processing
% }
% \experience{How vectorizing business-critical entities help solve operational problems}{Aug 2018}{}{
%     \noindent  \newline Institute for Natural Language Processing
% }

% \experience{How vectorizing business-critical entities help solve operational problems}{Aug 2019}{}{
%     \noindent  \newline Indian Institute of Management Bangalore (BAICONF-2019)
% }
% -
% ---- Awards -----
\section{Awards}

\experience{Mercedes-Benz R \& D India }{Innovation Award at Mercedes-Benz Analytics}{}{Oct 2019}{
}

\experience{ Mercedes-Benz R \& D India }{Outstanding Performer at Mercedes-Benz Analytics}{}{Dec 2019}{
}

\experience{Cisco Systems}{You Amaze Award for Outstanding Performance}{}{Oct 2021}{
}
% ----- Language \section{Language Skills}-----
\section{Language Skills}
 {English (C1) | Hindi (C1) | Kannada (C2) | German (A1) | Sanskrit (Hobby)}
\end{document}
